Tor's Usability for Censorship Circumvention

### 2015-10-05 paper/circumvention-experiment.tex
updated censorship environment simulation section

@@

\begin{figure}[t]
  \centering
    \includegraphics[width=0.5\textwidth]{configuration-screenshot.png}
    \caption{The Tor Bridges Configuration window of the Tor configuration interface. Tor users in censored environments and some of our participants will be required to select the correct bridge for circumventing censorship. Note that the interface prompts users to choose a transport type, which can be the source of confusion. Bridges are non-listed guard relays to the Tor network, and some of them can have transport types which obfuscate traffic in different ways.}
\end{figure}

@@

\noindent {\bfseries Censorship Environment Simulation} 
{\color{red}
We plan to simulate three censorship environments.
They are informed by our experience with pluggable transports
and knowledge of commonly seen censorship techniques.
They are not meant perfectly to replicate the network environment
in any particular country; rather, they are abstract simulations
that are nevertheless inspired by reality.

% talk about how these censorship environments cover the UI path

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item{Corporate network.}
A simulation of an enterprise or educational firewall.
Blocks all services but HTTP, HTTPS, and DNS.
Certain non-work-related domains, like youtube.com and torproject.org,
are blocked by DNS and HTTP inspection.
Blocked requests are redirected to a block page.
\item{DNS-only censor.}
This censor injects false replies to DNS queries
for forbidden domain names (DNS poisoning),
but does not do deep packet inspection on TCP streams.
Unlike the corporate censor, this censor allows protocols
outside a small whitelisted set.
\item{Comprehensive censor.}
Employs a variety of techniques, depending on the target.
May do DNS poisoning, IP blocking, and inspection of TCP streams
(examining the URL of HTTP requests, for example).
Some domains may be blocked by DNS and deep packet inspection;
others may additionally be blocked by IP address.
Tor relays are blocked by IP address.
Some domains, like wikipedia.org, may allow HTTP but not HTTPS.
Blocked requests fail silently (no block page).
\end{itemize}

In certain real censorship environment and our most 
prohibitive simulated censorship environments, only some of 
Tor's pluggable transports work in censorship environments
where others do not. Some of them require additional information
(like bridge addresses) before they work. Currently, we do not 
have a way to target test specific transports. However, we 
do ask why participants chose a specific pluggable 
transport in our exit survey to gain some insight.}\\

@@

%%  FROM ANONYMITY UX STUDY 
Our online artifacts of study of Tor as an anonymity tool, such as 
the summary, results, and resulting browser changes are below:
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \href{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}{blog post summary}
\item \href{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}{changes made to Tor}
\item \href{https://people.torproject.org/~dcf/uxsprint2015/}{subtitled screen videos}
\end{itemize}

>>>>

% setting up the environment wrt interface paths.
% setting up motivation: roleplay, tasks to complete
% follow up with a survey

@@

\begin{figure}[t]
\label{fig:bridges}
  \centering
    \includegraphics[width=0.5\textwidth]{configuration-screenshot.png}
    \caption{The Tor Bridges Configuration window of the Tor configuration interface. Tor users in censored environments and some of our participants will be required to select the correct bridge for circumventing censorship. Note that the interface prompts users to choose a transport type, which can be the source of confusion. Bridges are non-listed guard relays to the Tor network, and some of them can have transport types which obfuscate traffic in different ways.}
\end{figure}

@@

\noindent {\bfseries Censorship Environment Simulation} 
We plan to simulate three censorship environments.
They are informed by our experience with pluggable transports
and knowledge of commonly seen censorship techniques.
They are not meant perfectly to replicate the network environment
in any particular country. Although inspired by reality, these
abstract simulations are intended to require distinct configurations
of the Tor Browser from our participants.

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Mild censorship} 
(Reflective of countries such as {\color{red}?? and ??}.)
Certain domain names are blocked. Reaching these 
domains requires any use of a censorship circumvention 
tool. The default option to ``connect'' to the Tor network 
directly will circumvent this censor. Additional correct
bridge or proxy configuration are optional. 
\item {\bfseries Intermediate censorship} 
(Reflective of countries such as {\color{red}?? and ??}.)
Certain domain names are blocked. Censorship circumvention
tools are blocked. Since Tor is blocked by blocking all public Tor
relay nodes, the default option to ``connect'' to the Tor network
directly will fail. A choice of a hard-coded bridge (see Figure ~\ref{fig:bridges})
or a valid non-public bridge is required to circumvent this censor.  
Additional correct proxy configuration is optional.
\item {\bfseries Comprehensive censorship} 
(Reflective of countries such as China and Syria.)
Certain domain names are blocked. Censorship circumvention tools
are thoroughly blocked. Tor is blocked by blocking all public
Tor relay nodes, and the censor has examined source code to block
all hard-coded bridge relays in the configuration interface. The default option
to ``connect'' to the Tor network directly will fail. Choosing any other bridges than
``meek-amazon,'' ``meek-azure,'' and``meek-google,'' will fail. This is because 
domain-fronting requires censors to block entire CDNs to also block this
transport (which will cause huge collateral blocking damage), making it resistant to agressive censorship environments. Additional details,
see ~\cite{fifield2015blocking}.\\
\end{itemize}

@@

% from anonymity study
Our online artifacts of study of Tor as an anonymity tool, such as 
the summary, results, and resulting browser changes are below:
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \href{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}{blog post summary}
\item \href{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}{changes made to Tor}
\item \href{https://people.torproject.org/~dcf/uxsprint2015/}{subtitled screen videos}
\end{itemize}
